### 2018-07-04 paper/sphinxes.tex
Adds beginning of Sphinx description

\section{Sphinxes: the Sphinx header format for multi-node layers}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes.

>>>>

\section{Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.

\subsection{The Sphinx header format}

\NewVariable{\sk}{sk}
\NewVariable{\pk}{pk}

Each node \(n\) in the system has a public-key pair: private key \(\sk_n\in 
  \ZZ_q^*\) and public key \(\pk_n = g^{\sk_n}\in G\), where \(g\) generates a 
group \(G\) of prime order \(q\).

The Sphinx header is a triple \((\alpha_1, \beta_1, \gamma_1)\), where 
\(\alpha_1\) is \iac{DHKE} exponent (\(g^x\)), \(\beta_1\) is the encrypted 
routing data and \(\gamma_1\) is \iac{MAC} for \(\beta_1\).
The payload data, \(\delta\), is treated separately from the header.

The first node in the path, with keys \((\pk_1, \sk_1)\), will compute the 
shared secret \(s_1 = \alpha_1^{\sk_1}\), \ie complete the \ac{DHKE} round.
Since \(\pk_1\) is an authenticated key, the sender can be sure that only this 
particular node can process the first layer of the onion.

The derived shared secret \(s_1\) is then used to derive various keys.
One of them is the key for the \ac{MAC} (\(gamma_1\)) to verify the integrity 
of the header (\(\beta_1\)).
If \(\beta_1\) is correct, another key is derived from \(s_1\) to decrypt 
\(\beta_1\).

\subsection{The Sphinxes extension}

\dots
